Effective collector efficiency of sparse and dense arrays of emergent cylindrical collectors in laminar-turbulent transitional flows

### 2020-10-21 drafts/draft.tex
Done with param table
Updates from Overleaf

In our experiments, we modeled the effect of flow through a stand of roughly uniformly-spaced rigid, emergent collectors on direct interception of suspended sediment. We conducted our experiments in the Ecogeomorphology flume, a laboratory recirculating flume, located in McCone Hall at the University of California, Berkeley (Figure \ref{fig:floorplan}). The flume has a 5.25 m long by 0.6 m wide open-channel section with a rectangular channel cross-sectional geometry and smooth bed and walls. At the downstream outlet, a pump propelled water and suspended load through a pipe routing the mixture back to the upstream end of the open channel through a honeycomb flow collimator. Rotating discs in the pump entrain fluid and suspended particles through the pipe by viscous drag, minimizing any uncontrolled alteration of suspended particles outside of the open channel (REF Discflo manual explaining the principle of operation). The flume design maintains constant discharge through the open channel.

@@

We chose to use granular walnut shell flour to simulate sediment for our experiments because of the availability of homogeneous, sieve-measured grain sizes in suitable quantities. We performed preliminary experiments with a range of grain sizes but settled on WF5-200 as an appropriate match for sediment sizes in natural floodplains. We measured the distribution of particle size using a LISST-Portable XR laser interferometer (Sequoia Scientific Inc, Bellevue, WA). Median particle size was determined to be approximately \SI{25}{\micro\metre} (Figure \ref{fig:sedsize}).

>>>>

In our experiments, we modeled the effect of flow through a stand of roughly uniformly-spaced rigid, emergent collectors on direct interception of suspended sediment. We conducted our experiments in the Ecogeomorphology flume, a laboratory recirculating flume, located in McCone Hall at the University of California, Berkeley (Figure \ref{fig:floorplan}). The flume has a 5.25 m long by 0.6 m wide open-channel section with a rectangular channel cross-sectional geometry and a smooth bed and walls. At the downstream outlet, a pump propelled water and suspended load through a pipe routing the mixture back to the upstream end of the open channel through a honeycomb flow collimator. Rotating discs in the pump entrain fluid and suspended particles through the pipe by viscous drag, minimizing any uncontrolled alteration of suspended particles outside of the open channel (REF Discflo manual explaining the principle of operation). The flume design maintains constant discharge through the open channel.

@@

We chose to use granular walnut shell flour to simulate sediment for our experiments because of the availability of homogeneous, sieve-measured grain sizes in suitable quantities. We performed preliminary experiments with a range of grain sizes but settled on WF5-200 as an appropriate match for sediment sizes in natural floodplains. We measured the distribution of particle size using a LISST-Portable XR laser-scattering device (Sequoia Scientific Inc, Bellevue, WA). Median particle size was determined to be approximately \SI{25}{\micro\metre} (Figure \ref{fig:sedsize}).
